Halo alignments with large scale tidal and velocity fields

### 2013-05-15 paper/main.tex
extending the table with the summary

TABLA
\begin{table*}
\begin{tabular}{ccccccc}\hline\hline
Author & Web Method & Halo Finder & Spatial Scale & Test Direction &
Alignment & Mass dependence\\\hline
\cite{Hahn2007} & Tidal Web & FOF & $2.1$\hMpc & along
the filament & $-$& none\\
\cite{Hahn2007} & Tidal Web & FOF & $2.1$\hMpc &
perpendicular to sheet & $-$$-$ & stronger $>10^{12}$\hMsun\\
\cite{Hatton2001} & Neighbors$^1$ & FOF & & & 0\\\hline\hline
\end{tabular}\\
\caption{Summary of previous theoretical results.
NOTES:
$^1$ They do not use a web finder method. They look for correlations
with neightborig structures on any escale.
Angular Momentum}
\end{table*}

@@

THe identification of the cosmic web is done on a grid of $256^3$ with
a gaussian smoothing of $\sim 1$\hMpc over the velocity field. The
details of this smoothing are different from ours. This is decribed in
detail in the Appendix.

@@

The simulation is the millennium simulation, which has $2160^3$
particles in a volume of $500$\hMpc on a side. This corresponds to a
particle mass of $8.6\times 10^{8}$\hMsun. The catalog uses both halos
and subhalos which were identified with SUBFIND. Only halos with more
than 500 particles were kept to get a robust computation for the
spin. For each halo the spin is defined as the sum of the angular momentum
of each particle with respect to the center of mass.

>>>>

TABLA
\begin{table*}
\begin{tabular}{cccccc}\hline\hline
Author & Web Method & Spatial Scale & Test Direction &
Alignment & Mass dependence\\\hline

\cite{AragonCalvo2007} & Hessian density field & - &
perpendicular to sheet & $-$$-$ & $>10^{12}$\hMsun\\

& & - &
perpendicular to sheet & $-$ & $<10^{12}$\hMsun\\

& & - &
along the filament& $-$ & $>10^{12}$\hMsun\\

& & - &
along the filament& $+$ & $<10^{12}$\hMsun\\

\cite{Hahn2007} & Tidal Web & $2.1$\hMpc & along
the filament & $-$& none\\

& &  $2.1$\hMpc &
perpendicular to sheet & $-$$-$ & stronger $>10^{12}$\hMsun\\

\cite{Hatton2001} & Neighbors$^1$ &  & & 0\\\hline\hline

\end{tabular}\\
\caption{Summary of previous theoretical results.
NOTES:
$^1$ They do not use a web finder method. They look for correlations
with neightborig structures on any escale.
Angular Momentum}
\end{table*}

@@

The identification of the cosmic web is done on a grid of $256^3$ with
a gaussian smoothing of $\sim 1$\hMpc over the velocity field. We
define this velocity field as the ratio of a momentum density to the
matter density field. The details of this approach are described in
the Appendix .

@@

The simulation is the millennium run, which has $2160^3$
particles in a volume of $500$\hMpc on a side. This corresponds to a
particle mass of $8.6\times 10^{8}$\hMsun. The catalog uses both halos
and subhalos which were identified with SUBFIND. Only halos with more
than 500 particles were kept to get a robust computation for the
spin. For each halo the spin is defined as the sum of the angular
momentum of each particle with respect to the center of mass.
